---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nettskjema.tsd

<!-- badges: start -->
[![R-CMD-check](https://github.com/Athanasiamo/nettskjema.tsd/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Athanasiamo/nettskjema.tsd/actions/workflows/R-CMD-check.yaml)
[![CRAN status](https://www.r-pkg.org/badges/version/nettskjema.tsd)](https://CRAN.R-project.org/package=nettskjema.tsd)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- [![downloads](https://cranlogs.r-pkg.org/badges/last-month/nettskjema.tsd?color=blue)](https://r-pkg.org/pkg/nettskjema.tsd) -->
<!-- badges: end -->

Working with Nettskjema (<https://nettskjema.no/>) data inside TSD can be challenging. 
This package aims to aid users in managing their incoming Nettskjema data by decrypting the data and storing the nettskjema data and meta-data in convenient and standardised ways. 
This package functionality currently only works on the Linux VMs of TSD, and for version 1 of the nettskjema data delivery to TSD.

## Installation

You can install the development version of nettskjema.tsd from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Athanasiamo/nettskjema.tsd")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(nettskjema.tsd)
## basic example code
```

## Code of Conduct

Please note that the nettskjema.tsd project is released with a [Contributor Code of Conduct](https://athanasiamo.github.io/nettskjema.tsd/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
